% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt

\usepackage{hyperref}
%\usepackage{textcomp}
%\usepackage{enumitem}
 \usepackage[11pt]{moresize}
%\usepackage{helvetica} % uses helvetica postscript font (download
% helvetica.sty) \usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Ganindu Nanayakkara}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{%Mr. bootha banga \\
% Ghost busters HQ \\
% Ghost Corporation \\
% Rt. 56 \\
% Ghost town,  05867
SpaceX \\  Hawthorne, CA 90250
}

\begin{center}
{\large\bf Ganindu Nanayakkara} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
{Asian Institute of Technology \\   Klong Luang, Pathumthani\\ Thailand, 12120
\\ \url{ganindu@gmail.com}} \end{center} \vfill % forces letterhead to top of
% page


\opening{Dear Sir/Madam,} 
 
\noindent
I am a Mechatronics graduate$(2014)$ from the Asian Institute of Technology
(Bangkok), This letter and the attached CV serve as my application for the
position at SpaceX. 

\noindent
Maybe you hear this a lot. But I too have to confess that I'm also a fan of
Spacex and Tesla from the very early days. It is and was a great joy watching
the two companies grow to become great icons in the human achievement because I
was also a part of the few people who backed the great effort when people were
backing Industry giants those days and undermining the determination of you
guys who kicked off from the first principles to prove what it takes to achieve
such astronomical heights. And your feats encouraged me and possibly many other
students to do things beyond the scope of what we were asked to and I'm proud
to have inherited that will and thank you very much for all those reminders of
perseverance. Also I have to hand it over to you guys, Mr.Elon and also to
Mr.Steve Jurvertson who is also a great guy that loves rockets.

\noindent
Even though at this stage I'm supposed to say here How would I fit into SpaceX
in academic terms, honestly speaking I'd really do anything to work among such an innovative
cool bunch of people. I am a Mechatronics graduate and my most preferred area is
control systems and multiple-robot collaboration, control system development,
machine vision, Simulations and system optimization are the areas I like. But since I'm
a mechatronics engineer I can handle Mechanical, Electronics systems and power
systems as well. I have added short descriptions of some of my projects and
video links in my CV for further information. 

\noindent 
I would enjoy speaking with you further to discuss, in detail, how can I add
more value to SpaceX. And I how am always exited to learn new things, face new
challenges and work in my full capacity to achieve the best possible results. I
am very much eager to apply my energy to the intersting projects SpaceX has.
Please excuse me for the not so professional looking cover letter because I
guess this is what happens when people apply to their dream workplace.. 

 
\closing{Best,} 
 
%\encl{}					% Enclosures
\end{letter}
 

\end{document}
